Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-04-01 journal-draft/bare_jrnl_comsoc.tex
modified section 3

\section{Centralized Solution for Robust Clustering}
\label{centralized_solution}
When the global knowledge of the CRN is available to us, we can propose a centralized scheme as comparison.
The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem, then the latter is solved with standard software packages.
The optimization searches the set $\mathcal{S}$ and decides on the clusters according to the following optimization formulation,
%
%which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
%Then, a central node (or controller) with the knowledge of all CR nodes (and also the possible clusters) can solve the problem based on the following formulation. 
%
%Second, we assign a cluster size related weight to each cluster, which is positively correlated with the difference between the cluster size and the desired cluster size.

@@

\begin{equation}
\begin{aligned}
     &\max\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i\cdot t_{ij}) \\
     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot w_i,\, for\,\,\forall i=1, \ldots, M \\
  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
This problem is a binary linear programming problem, which can be solved by many available solvers.
$w_i$ and $x_{ij}$ are two binary variables.
% where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
%$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
Being either 1 or 0, $w_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
%Node index $j$ is identical to the node ID.
$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of possible clusters in $\mathcal{S}$.

@@

%The optimization is a binary linear programming problem.
The objective is to maximize the sum of the numbers of CCs in the clusters which constitute the whole CRN.
$t_{ij}$ is a constant and there is,
%In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
%
%
%Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{potential} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
%Potential clusters are the clusters which satisfy the conditions introduced in Section~\ref{sec:model}. 
%Note that the potential clusters include the singleton ones.
%By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.

\begin{equation}
t_{ij} = \frac{q_{ij}}{|C_i|} - p_i(C_i)
\end{equation}
where $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
%$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
$p_i(C_i)$ is the size-related weight, which reflects the deviation between the size of $C_i$ and the desired size.
Assuming $\delta$ is the desired size, then
$$
p_i(C_i) = \left\{ \begin{array}{rl}
0 &\mbox{ if $|C_i|=\delta$} \\
\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
\vdots
\end{array} \right.
$$
where $\rho_1, \rho_2, \cdots$ are positive values and these is $\rho_2> \rho_1>0$.

@@

Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
Replacing $t_{ij}$ with $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
\begin{equation}
\begin{aligned}
     &\max\limits_{w_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (w_i\cdot \frac{q_{ij}}{|C_i|} - w_i\cdot p_i(C_i)) \\
\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
The sum of the first items is the sum of CCs of all the chosen clusters.
As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.

@@

The difficulty of using this method lies in obtaining the set $\mathcal{S}$.
In the worst case, \ie the CRN forms a full connected graph, the size of $\mathcal{S}$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
%To levitate this problem, a smaller set, \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
%In this case, the global optimal may not be found.
%$\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.

Another obstacle to apply this centralized scheme comes from the characteristics of CRN.
In order to apply this scheme in practice, a large over head needs to be factored in in collecting the channel usage as seen by the R nodes, as well as the connectivity between the CR nodes.
After computing the clustering solution, the centralized node needs to distribute it across the whole network.

In CRN, it is necessary to do clustering again on some occasions.
For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CCs in these clusters don't exist any longer due to primary users' activity. 
Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.

@@

\begin{center}
\begin{table*}[!htb]
\caption{Signalling overhead}\label{tab_overhead}
{\renewcommand{\arraystretch}{1.15} %<- modify value to suit your needs
{\small
\hfill{}
\begin{threeparttable}
\begin{tabular}{|C{2 cm}|C{2.8 cm}|C{3.15 cm}|C{7.7 cm}|}
\hline
 Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
 ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability on all cluster members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
 ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
 SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members, which is $|C(i)| |\mathcal{K}|$ bytes
 \\ \hline
 Centralized			&$\mathcal{O}(N)$			&	$N + n + m$ (upper bound) \cite{Efficient_broadcasting_gathering_adhoc}		& clustering result, which is 2$N$ bytes \tnotex{tnote:robots-r1} 					\\ \hline
\end{tabular}
    \begin{tablenotes}
      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of $\{i, C\}, i\in C, i\in \mathcal{N}$.
    \end{tablenotes}
    \end{threeparttable}
}
}
\hfill{}
\end{table*}
\end{center}

>>>>

\section{Centralized Solution for Robust Clustering}
\label{centralized_solution}
When the global knowledge of the CRN is available to us, we can propose a centralized scheme as comparison.
The proposed centralized solution formulates the problem in Definition~\ref{def_centralized_clustering} as an optimization problem which is solved with standard software packages.
The optimization searches the set $\mathcal{S}$ and decides on the clusters according to the following optimization formulation,
%
%which constitute the whole CRN without overlapping between any two of them, besides, the sum of CCs of the chosen clusters is maximized.
%Then, a central node (or controller) with the knowledge of all CR nodes (and also the possible clusters) can solve the problem based on the following formulation. 
%
%Second, we assign a cluster size related weight to each cluster, which is positively correlated with the difference between the cluster size and the desired cluster size.

@@

\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot t_{ij}) \\
     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, for\,\,\forall i=1, \ldots, M \\
  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
This problem is a binary linear programming problem, which can be solved by many available solvers.
$y_i$ and $x_{ij}$ are two binary variables.
% where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
%$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
%Node index $j$ is identical to the node ID.
$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of clusters in $\mathcal{S}$.

@@

%The optimization is a binary linear programming problem.
The objective is to maximize the sum of the numbers of CCs in the clusters which constitute the CRN.
$t_{ij}$ is a constant and there is
%In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
%
%
%Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{potential} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
%Potential clusters are the clusters which satisfy the conditions introduced in Section~\ref{sec:model}. 
%Note that the potential clusters include the singleton ones.
%By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.

\begin{equation}
t_{ij} = \frac{q_{ij}}{|C_i|} - p_i(C_i)
\end{equation}
where constant $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
%$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
$p_i(C_i)$ is the size-related weight, which reflects the deviation of $C_i$'s size from the desired size.
Assuming $\delta$ is the desired size, then there is
$$
p_i(C_i) = \left\{ \begin{array}{rl}
0 &\mbox{ if $|C_i|=\delta$} \\
\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
\vdots
\end{array} \right.
$$
where $\rho_1, \rho_2, \cdots$ are positive values and these is $\rho_2> \rho_1>0$.

@@

%Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
When $t_{ij}$ is replaced with $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p_i(C_i)) \\
\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
The sum of the first items is the sum of CCs of all the chosen clusters.
As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.

@@

The difficulty of using this method lies in obtaining the set $\mathcal{S}$.
In the worst case, \ie the CRN forms a full connected graph, the size of $\mathcal{S}$ is $\Sigma_{r=1}^{N}\ {N \choose r} = 2^N-1$.
%To levitate this problem, a smaller set, \ie $\mathcal{G} \subset \mathcal{S}$ can be used.
%In this case, the global optimal may not be found.
%$\mathcal{G}$ can be prepared based on the cluster size, and it is recommended to include all the singleton clusters to make sure the availability of feasible solutions.
Another obstacle comes from the fact that the centralized controller needs to be reliable at anytime, which is a challenge for CRN as the spectrum on the controller can not be guaranteed.
%In order to apply this scheme in practice, a large over head needs to be factored in in collecting the channel usage as seen by the R nodes, as well as the connectivity between the CR nodes.
%After computing the clustering solution, the centralized node needs to distribute it across the whole network.

%In CRN, it is necessary to do clustering again on some occasions.
%For example, when a certain amount of CR users move away from their clusters, \ie they loose the direction connection with any member in their previous clusters, or a certain amount of clusters can not be maintained as the CCs in these clusters don't exist any longer due to primary users' activity. 
%Hence, when the spectrum availability and the CR users' location change frequently, the centralized robust clustering scheme is not suitable for CRN.

@@

\begin{center}
\begin{table*}[!htb]
\caption{Signalling overhead}\label{tab_overhead}
{\renewcommand{\arraystretch}{1.15} %<- modify value to suit your needs
{\small
\hfill{}
\begin{threeparttable}
\begin{tabular}{|C{2 cm}|C{2.8 cm}|C{3.15 cm}|C{7.7 cm}|}
\hline
 Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
 ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability on all cluster members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
 ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
 SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members, which is $|C(i)| |\mathcal{K}|$ bytes
 \\ \hline
 Centralized			&$\mathcal{O}(N)$			&	$N + n + m$ (upper bound) 		& clustering result, which is 2$N$ bytes \tnotex{tnote:robots-r1} 					\\ \hline
\end{tabular}
    \begin{tablenotes}
      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of $\{i, C\}, i\in C, i\in \mathcal{N}$.
    \end{tablenotes}
    \end{threeparttable}
}
}
\hfill{}
\end{table*}
\end{center}
